---
title: "Statistical Analyses Script"
author: "Karlis"
date: "2024-06-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Libraries
library(tidyverse)
library(readxl)
library(questionr)
library(knitr)
library(kableExtra)

library(colorspace)
library(sf)
library(viridis)
library(labelled)
library(ggrepel)
library(marmap)
library(ggspatial)
library(cowplot)

```



```{r echo=FALSE, message=FALSE, warning=FALSE}
# Work directory
setwd("C:/Users/SITAPHA/Documents/Travaux_Consultance/Karlhis YAO/Analyses_Karlis")

# Database
bd  <- read_excel("Base Karlhis.ok.xlsx")
#head(bd)
```

# Relationship between geographic localization and prevalence of Wolbachia in the population of Aedes aegypti
## Tests's results
```{r echo=FALSE, message=FALSE, warning=FALSE}

# Filtrage de la base de données
aegypti <- bd %>% filter(Species=="Aedes aegypti")

# Calcul des totaux
sex_table <- table(aegypti$Sex, aegypti$`Statut Wolbachia`)
localization_table <- table(aegypti$Gergraphic.localization, aegypti$`Statut Wolbachia`)

# Calcul des pourcentages
sex_table_percent <- prop.table(sex_table, 1) * 100
localization_table_percent <- prop.table(localization_table, 1) * 100

# Préparation des données pour le tableau
sex_summary <- as.data.frame.matrix(sex_table)
sex_summary$Negative <- paste0(sex_summary$Negative, " (", round(sex_table_percent[, "Negative"], 2), "%)")
sex_summary$Positive <- paste0(sex_summary$Positive, " (", round(sex_table_percent[, "Positive"], 2), "%)")

localization_summary <- as.data.frame.matrix(localization_table)
localization_summary$Negative <- paste0(localization_summary$Negative, " (", round(localization_table_percent[, "Negative"], 2), "%)")
localization_summary$Positive <- paste0(localization_summary$Positive, " (", round(localization_table_percent[, "Positive"], 2), "%)")

# Chi-square test pour le sexe
chi_square_sex <- chisq.test(sex_table, correct = FALSE)
chi_square_sex_result <- paste("Chi-squared:", round(chi_square_sex$statistic, 5))

# Fisher's exact test pour la localisation
fisher_exact_localization <- fisher.test(localization_table)
fisher_exact_localization_result <- paste("OR =", round(fisher_exact_localization$estimate, 5))

# Création du tableau
table_data <- rbind(
  c("Sex", "Female", sex_summary[1, "Negative"], sex_summary[1, "Positive"], chi_square_sex_result, 1, round(chi_square_sex$p.value, 4)),
  c("Sex", "Male", sex_summary[2, "Negative"], sex_summary[2, "Positive"], "", "", ""),
  c("Geographic localization", "North", localization_summary[1, "Negative"], localization_summary[1, "Positive"], fisher_exact_localization_result, "", round(fisher_exact_localization$p.value, 4)),
  c("Geographic localization", "South", localization_summary[2, "Negative"], localization_summary[2, "Positive"], "", "", "")
)

#colnames(table_data) <- c("Category", "Sub-category", "Chi-squared/Fisher’s exact", "df", "P-value")

# Affichage du tableau avec kable
table_data %>%
  kable("html", align = 'c', caption = "Relationship between sex/geographic localization and prevalence of Wolbachia in the population of Aedes aegypti") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```


## Frequencies's table
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Préparation des données pour le tableau
sex_summary <- as.data.frame.matrix(sex_table)
localization_summary <- as.data.frame.matrix(localization_table)

# Ajouter les pourcentages
sex_summary$Negative <- paste0(sex_summary$Negative, " (", round(sex_table_percent[, "Negative"], 2), "%)")
sex_summary$Positive <- paste0(sex_summary$Positive, " (", round(sex_table_percent[, "Positive"], 2), "%)")

localization_summary$Negative <- paste0(localization_summary$Negative, " (", round(localization_table_percent[, "Negative"], 2), "%)")
localization_summary$Positive <- paste0(localization_summary$Positive, " (", round(localization_table_percent[, "Positive"], 2), "%)")

# Combiner les tableaux
final_summary <- rbind(
  cbind(Variable = "Sex", Category = rownames(sex_summary), sex_summary),
  cbind(Variable = "Geographic localization", Category = rownames(localization_summary), localization_summary)
)

# Convertir en tableau formaté

final_summary %>%
  kable("html", align = 'c', caption = "Relationship between sex/geographic localization and prevalence of Wolbachia in the population of Aedes aegypti") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


# Relationship between sex/geographic localization and prevalence of Wolbachia in the population of Anophele gambiae s.l.
## Tests's results
```{r echo=FALSE, message=FALSE, warning=FALSE}

# Filtrage de la base de données
Anophele_gambiae <- bd %>% filter(Species=="Anophele gambiae")

# Calcul des totaux
sex_table <- table(Anophele_gambiae$Sex, Anophele_gambiae$`Statut Wolbachia`)
localization_table <- table(Anophele_gambiae$Gergraphic.localization, Anophele_gambiae$`Statut Wolbachia`)

# Calcul des pourcentages
sex_table_percent <- prop.table(sex_table, 1) * 100
localization_table_percent <- prop.table(localization_table, 1) * 100

# Préparation des données pour le tableau
sex_summary <- as.data.frame.matrix(sex_table)
sex_summary$Negative <- paste0(sex_summary$Negative, " (", round(sex_table_percent[, "Negative"], 2), "%)")
sex_summary$Positive <- paste0(sex_summary$Positive, " (", round(sex_table_percent[, "Positive"], 2), "%)")

localization_summary <- as.data.frame.matrix(localization_table)
localization_summary$Negative <- paste0(localization_summary$Negative, " (", round(localization_table_percent[, "Negative"], 2), "%)")
localization_summary$Positive <- paste0(localization_summary$Positive, " (", round(localization_table_percent[, "Positive"], 2), "%)")

# Chi-square test pour le sexe
chi_square_sex <- chisq.test(sex_table, correct = FALSE)
chi_square_sex_result <- paste("Chi-squared:", round(chi_square_sex$statistic, 5))

# Fisher's exact test pour la localisation
fisher_exact_localization <- fisher.test(localization_table)
fisher_exact_localization_result <- paste("OR =", round(fisher_exact_localization$estimate, 5))

# Création du tableau
table_data <- rbind(
  c("Sex", "Female", sex_summary[1, "Negative"], sex_summary[1, "Positive"], chi_square_sex_result, 1, round(chi_square_sex$p.value, 4)),
  c("Sex", "Male", sex_summary[2, "Negative"], sex_summary[2, "Positive"], "", "", ""),
  c("Geographic localization", "North", localization_summary[1, "Negative"], localization_summary[1, "Positive"], fisher_exact_localization_result, "", round(fisher_exact_localization$p.value, 4)),
  c("Geographic localization", "South", localization_summary[2, "Negative"], localization_summary[2, "Positive"], "", "", "")
)

#colnames(table_data) <- c("Category", "Sub-category", "Chi-squared/Fisher’s exact", "df", "P-value")

# Affichage du tableau avec kable
table_data %>%
  kable("html", align = 'c', caption = "Relationship between sex/geographic localization and prevalence of Wolbachia in the population of Anophele gambiae") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```


## Frequencies's table
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Préparation des données pour le tableau
sex_summary <- as.data.frame.matrix(sex_table)
localization_summary <- as.data.frame.matrix(localization_table)

# Ajouter les pourcentages
sex_summary$Negative <- paste0(sex_summary$Negative, " (", round(sex_table_percent[, "Negative"], 2), "%)")
sex_summary$Positive <- paste0(sex_summary$Positive, " (", round(sex_table_percent[, "Positive"], 2), "%)")

localization_summary$Negative <- paste0(localization_summary$Negative, " (", round(localization_table_percent[, "Negative"], 2), "%)")
localization_summary$Positive <- paste0(localization_summary$Positive, " (", round(localization_table_percent[, "Positive"], 2), "%)")

# Combiner les tableaux
final_summary <- rbind(
  cbind(Variable = "Sex", Category = rownames(sex_summary), sex_summary),
  cbind(Variable = "Geographic localization", Category = rownames(localization_summary), localization_summary)
)

# Convertir en tableau formaté

final_summary %>%
  kable("html", align = 'c', caption = "Relationship between sex/geographic localization and prevalence of Wolbachia in the population of Anophele gambiae") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


# Relationship between sex/geographic localization and prevalence of Wolbachia in the population of Culex quinquefasciatus
## Tests's results
```{r echo=FALSE, message=FALSE, warning=FALSE}

# Filtrage de la base de données
Culex_quinquefasciatus <- bd %>% filter(Species=="Culex quinquefasciatus")

# Calcul des totaux
sex_table <- table(Culex_quinquefasciatus$Sex, Culex_quinquefasciatus$`Statut Wolbachia`)
localization_table <- table(Culex_quinquefasciatus$Gergraphic.localization, Culex_quinquefasciatus$`Statut Wolbachia`)

# Calcul des pourcentages
sex_table_percent <- prop.table(sex_table, 1) * 100
localization_table_percent <- prop.table(localization_table, 1) * 100

# Préparation des données pour le tableau
sex_summary <- as.data.frame.matrix(sex_table)
sex_summary$Negative <- paste0(sex_summary$Negative, " (", round(sex_table_percent[, "Negative"], 2), "%)")
sex_summary$Positive <- paste0(sex_summary$Positive, " (", round(sex_table_percent[, "Positive"], 2), "%)")

localization_summary <- as.data.frame.matrix(localization_table)
localization_summary$Negative <- paste0(localization_summary$Negative, " (", round(localization_table_percent[, "Negative"], 2), "%)")
localization_summary$Positive <- paste0(localization_summary$Positive, " (", round(localization_table_percent[, "Positive"], 2), "%)")

# Chi-square test pour le sexe
chi_square_sex <- chisq.test(sex_table, correct = FALSE)
chi_square_sex_result <- paste("Chi-squared:", round(chi_square_sex$statistic, 5))

# Fisher's exact test pour la localisation
chi_square_localization <- chisq.test(localization_table)
chi_square_localization_result <- paste("OR =", round(chi_square_localization$statistic, 5))

# Création du tableau
table_data <- rbind(
  c("Sex", "Female", sex_summary[1, "Negative"], sex_summary[1, "Positive"], chi_square_sex_result, 1, round(chi_square_sex$p.value, 4)),
  c("Sex", "Male", sex_summary[2, "Negative"], sex_summary[2, "Positive"], "", "", ""),
  c("Geographic localization", "North", localization_summary[1, "Negative"], localization_summary[1, "Positive"], chi_square_localization_result, "", round(chi_square_localization$p.value, 4)),
  c("Geographic localization", "South", localization_summary[2, "Negative"], localization_summary[2, "Positive"], "", "", "")
)


# Affichage du tableau avec kable
table_data %>%
  kable("html", align = 'c', caption = "Relationship between sex/geographic localization and prevalence of Wolbachia in the population of Culex quinquefasciatus") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```


## Frequencies's table
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Préparation des données pour le tableau
sex_summary <- as.data.frame.matrix(sex_table)
localization_summary <- as.data.frame.matrix(localization_table)

# Ajouter les pourcentages
sex_summary$Negative <- paste0(sex_summary$Negative, " (", round(sex_table_percent[, "Negative"], 2), "%)")
sex_summary$Positive <- paste0(sex_summary$Positive, " (", round(sex_table_percent[, "Positive"], 2), "%)")

localization_summary$Negative <- paste0(localization_summary$Negative, " (", round(localization_table_percent[, "Negative"], 2), "%)")
localization_summary$Positive <- paste0(localization_summary$Positive, " (", round(localization_table_percent[, "Positive"], 2), "%)")

# Combiner les tableaux
final_summary <- rbind(
  cbind(Variable = "Sex", Category = rownames(sex_summary), sex_summary),
  cbind(Variable = "Geographic localization", Category = rownames(localization_summary), localization_summary)
)

# Convertir en tableau formaté

final_summary %>%
  kable("html", align = 'c', caption = "Relationship between sex/geographic localization and prevalence of Wolbachia in the population of Culex quinquefasciatus") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


# Relationship between sex and prevalence of Wolbachia in the population of Culex tigripes
## Tests's results
```{r echo=FALSE, message=FALSE, warning=FALSE}

# Filtrage de la base de données
Culex_tigripes <- bd %>% filter(Species=="Culex tigripes")

# Calcul des totaux
sex_table <- table(Culex_tigripes$Sex, Culex_tigripes$`Statut Wolbachia`)

# Calcul des pourcentages
sex_table_percent <- prop.table(sex_table, 1) * 100

# Préparation des données pour le tableau
sex_summary <- as.data.frame.matrix(sex_table)
sex_summary$Negative <- paste0(sex_summary$Negative, " (", round(sex_table_percent[, "Negative"], 2), "%)")
sex_summary$Positive <- paste0(sex_summary$Positive, " (", round(sex_table_percent[, "Positive"], 2), "%)")



# Fisher test pour le sexe
fisher_sex <- fisher.test(sex_table)
fisher_sex
```


## Frequencies's table
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Préparation des données pour le tableau
sex_summary <- as.data.frame.matrix(sex_table)
#localization_summary <- as.data.frame.matrix(localization_table)

# Ajouter les pourcentages
sex_summary$Negative <- paste0(sex_summary$Negative, " (", round(sex_table_percent[, "Negative"], 2), "%)")
sex_summary$Positive <- paste0(sex_summary$Positive, " (", round(sex_table_percent[, "Positive"], 2), "%)")



# Combiner les tableaux
final_summary <-   cbind(Variable = "Sex", Category = rownames(sex_summary), sex_summary)

# Convertir en tableau formaté

final_summary %>%
  kable("html", align = 'c', caption = "Relationship between sex prevalence of Wolbachia in the population of Culex tigripes") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


# Relationship between sex and prevalence of Wolbachia in the population of Culex theilleri
## Tests's results
```{r echo=FALSE, message=FALSE, warning=FALSE}

# Filtrage de la base de données
Culex_theileri <- bd %>% filter(Species=="Culex theileri")

# Calcul des totaux
sex_table <- table(Culex_theileri$Sex, Culex_theileri$`Statut Wolbachia`)

# Calcul des pourcentages
sex_table_percent <- prop.table(sex_table, 1) * 100

# Préparation des données pour le tableau
sex_summary <- as.data.frame.matrix(sex_table)
sex_summary$Negative <- paste0(sex_summary$Negative, " (", round(sex_table_percent[, "Negative"], 2), "%)")
sex_summary$Positive <- paste0(sex_summary$Positive, " (", round(sex_table_percent[, "Positive"], 2), "%)")



# Fisher test pour le sexe
fisher_sex <- fisher.test(sex_table)
fisher_sex
```



## Frequencies's table
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Préparation des données pour le tableau
sex_summary <- as.data.frame.matrix(sex_table)
localization_summary <- as.data.frame.matrix(localization_table)

# Ajouter les pourcentages
sex_summary$Negative <- paste0(sex_summary$Negative, " (", round(sex_table_percent[, "Negative"], 2), "%)")
sex_summary$Positive <- paste0(sex_summary$Positive, " (", round(sex_table_percent[, "Positive"], 2), "%)")


# Combiner les tableaux
final_summary <- cbind(Variable = "Sex", Category = rownames(sex_summary), sex_summary)
 

# Convertir en tableau formaté

final_summary %>%
  kable("html", align = 'c', caption = "Relationship between sex prevalence of Wolbachia in the population of Culex theileri") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


# Relationship between sex and prevalence of Wolbachia in the population of all mosquito species

## Tests's results
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Calcul des totaux
sex_table <- table(bd$Sex, bd$`Statut Wolbachia`)

# Calcul des pourcentages
sex_table_percent <- prop.table(sex_table, 1) * 100

# Préparation des données pour le tableau
sex_summary <- as.data.frame.matrix(sex_table)
sex_summary$Negative <- paste0(sex_summary$Negative, " (", round(sex_table_percent[, "Negative"], 2), "%)")
sex_summary$Positive <- paste0(sex_summary$Positive, " (", round(sex_table_percent[, "Positive"], 2), "%)")


# Chi-square test pour le sexe
chi_square_sex <- chisq.test(sex_table,, correct = FALSE)
chi_square_sex

```


## Frequencies's table
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Préparation des données pour le tableau
sex_summary <- as.data.frame.matrix(sex_table)

# Ajouter les pourcentages
sex_summary$Negative <- paste0(sex_summary$Negative, " (", round(sex_table_percent[, "Negative"], 2), "%)")
sex_summary$Positive <- paste0(sex_summary$Positive, " (", round(sex_table_percent[, "Positive"], 2), "%)")


# Combiner les tableaux
final_summary <- cbind(Variable = "Sex", Category = rownames(sex_summary), sex_summary)


# Convertir en tableau formaté

final_summary %>%
  kable("html", align = 'c', caption = "Relationship between sex prevalence of Wolbachia in the population for all mosquito species") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


# Cartogaphy
```{r echo=FALSE, message=FALSE, warning=FALSE}
### Shapefiles
adm1 <- read_sf("shapefiles/civadm1.shp", quiet = TRUE)
adm2 <- read_sf("shapefiles/civadm2.shp", quiet = TRUE)
adm3 <- read_sf("shapefiles/civadm3.shp", quiet = TRUE)

```


```{r echo=FALSE, message=FALSE, warning=FALSE}
# Cartographie
## Côte d'Ivoire
crtt <- ggplot(data = adm1) + 
  geom_sf( color = "black", linewidth = 0.2,fill = "white")  +
  #geom_sf(data = adm3, color="white", linewidth = 0.9) +
  geom_sf(data = subset(adm3, ADM3_FR == "Bouaké"), fill = "red", color = "black") +
  geom_sf(data = subset(adm3, ADM3_FR == "Boundiali"), fill = "red", color = "black") +
  geom_sf(data = subset(adm3, ADM3_FR == "Abidjan"), fill = "red", color = "black") +
  geom_sf(data = subset(adm3, ADM3_FR == "Korhogo"), fill = "red", color = "black") +
  geom_sf(data = subset(adm3, ADM3_FR == "Bingerville"), fill = "red", color = "black") +
  theme_void()+ 
  labs(title = "Ivory Cost")+theme_void()

bd$Longitude <- as.numeric(bd$Longitude)
bd$Latitude <- as.numeric(bd$Latitude)

## Bouaké
Bouak <- filter(adm3,ADM3_FR=="Bouaké")
bouak = ggplot(data=Bouak)+
  geom_sf( color="black", fill="white")+
  geom_sf_label(aes(label=ADM3_FR),nudge_x = 0.1,
                nudge_y = 0.23, size=3)+ 
  geom_jitter(data=(filter(bd,ADM3_FR=="Bouaké")%>% distinct(Species,`Capture_site`,.keep_all = TRUE)),
              aes(x = Longitude,y=Latitude, shape=`Capture_site`,
                  color=Species), size=2,width = 0.1, height  = 0.1)+theme_void()+
  theme(legend.position = "none")





## Boundiali
Boundiali <- filter(adm3,ADM3_FR=="Boundiali")
boundiali = ggplot(data=Boundiali)+
  geom_sf( color="black", fill="white")+
  geom_sf_label(aes(label=ADM3_FR),nudge_x = 0.1,
                nudge_y = 0.23, size=3) +
  geom_jitter(data=(filter(bd,ADM3_FR=="Boundiali")%>% distinct(Species,`Capture_site`,.keep_all = TRUE)),
                          aes(x = Longitude-0.03,y=Latitude, shape=`Capture_site`,
                              color=Species), size=2,width = 0.1, height  = -0.18)+
  theme_void()+theme(legend.position = "none")



## Abidjan
Abidjan <- filter(adm3,ADM3_FR=="Abidjan")
abidjan = ggplot(data=Abidjan)+
  geom_sf( color="black", fill="white")+
  geom_sf_label(aes(label=ADM3_FR),nudge_x = 0.009,
                nudge_y = 0.2, size=3) +
  geom_jitter(data=(filter(bd,ADM3_FR=="Abidjan")%>% distinct(Species,`Capture_site`,.keep_all = TRUE)),
                                  aes(x = Longitude+0.04,y=Latitude, shape=`Capture_site`,
                                      color=Species), size=2,width = 0.01, height  = 0.01)+
  theme_void()+theme(legend.position = "none")



## Bingerville
Bingerville <- filter(adm3,ADM3_FR=="Bingerville")
bingerville = ggplot(data=Bingerville)+
  geom_sf( color="black", fill="white")+
  geom_sf_label(data=Bingerville,aes(label=ADM3_FR),nudge_x = 0.085,
                nudge_y = 0.08, size=3)+
 geom_jitter(data=filter(bd,ADM3_FR=="Bingerville")%>% distinct(Species,`Capture_site`,.keep_all = TRUE),
       aes(x = Longitude,y=Latitude, shape=`Capture_site`,
         color=Species), size=2,width = 0.03, height  = 0.01)+
  theme_void()+theme(legend.position = "none")



## Korhogo
Korhogo <- filter(adm3,ADM3_FR=="Korhogo")
korhogo = ggplot(data=Korhogo)+
  geom_sf( color="black", fill="white")+
  geom_sf_label(aes(label=ADM3_FR),nudge_x = 0.082,
                nudge_y = 0.11, size=3) +
  geom_jitter(data=(filter(bd,ADM3_FR=="Korhogo")%>% 
                distinct(Species,`Capture_site`,.keep_all = TRUE)),
   aes(x = Longitude-0.05,y=Latitude+0.04, shape=`Capture_site`,
      color=Species), size=2,width = 0.03, height  = 0.03)+
  theme_void()+theme(legend.position = "none")#+coord_sf(xlim=c(-5.91,-5.533369),ylim=c(9.386580,9.63))



## Assemblage des cartes
arrow_angle_bfa = -50
arrow_length_bfa = 0.3
arrow_end_length_bfa <- unit(0.7, "cm")


pllt = plot_grid(plot_grid(boundiali,bouak,ncol=1),plot_grid(crtt,abidjan,
  ncol = 1,rel_widths = c(2,1),rel_heights = c(2,1),align = "hv"),
  plot_grid(korhogo,bingerville, ncol=1),ncol=3,rel_widths = c(1,2,1),
  rel_heights = c(2,1,2), align = "hv")+
  theme_light()+ geom_segment(aes(x = 0.46, y = 0.86, xend = 0.22, yend = 0.87), 
               arrow = arrow(angle = 30,length = unit(arrow_length_bfa, "cm"),ends="last",type = "closed"), color = "black", size = 0.6) + 
  geom_segment(aes(x = 0.5, y = 0.86, xend = 0.75, yend = 0.87), 
               arrow = arrow(angle = 30,length = unit(arrow_length_bfa, "cm"),ends="last",type = "closed"), color = "black", size = 0.6) + 
  geom_segment(aes(x = 0.5, y = 0.7, xend = 0.23, yend = 0.425), 
               arrow = arrow(angle = 30,length = unit(arrow_length_bfa, "cm"),ends="last",type = "closed"), color = "black", size = 0.6) + 
  geom_segment(aes(x = 0.55, y = 0.432, xend = 0.55, yend = 0.275), 
               arrow = arrow(angle = 30,length = unit(arrow_length_bfa, "cm"),ends="last",type = "closed"), color = "black", size = 0.6) + 
  geom_segment( aes(x = 0.57, y = 0.44, xend = 0.76, yend = 0.27), 
               arrow = arrow(angle = 30,length = unit(arrow_length_bfa, "cm"),ends="last",type = "closed"), color = "black", size = 0.6) + 
  labs(title= "Distribution of species by Capture site", hjust=0.5,caption = "Source : GADM\n Data : Wolbachia data \n Author : Sitapha KONATE") +
  geom_point(data=bd,aes(x = Longitude,y=Latitude, shape=`Capture_site`,color=Species))+theme(legend.position = "bottom")#+ warning(call. = FALSE)
pllt
```

# Barplot
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Manipulation des données
data_P.W_E <-  filter(bd, Species %in% c("Aedes aegypti","Anopheles gambiae s.l.", 
                                                       "Culex quinquefasciatus"))
  
  
db <- data_P.W_E %>% 
    dplyr::group_by(Gergraphic.localization, Species)%>% 
    dplyr::mutate(Tot = n()) #%>% 
  
  db <- db %>% 
    dplyr::group_by(Gergraphic.localization, Species, `Statut Wolbachia`)%>% 
    dplyr::mutate(effectif = n(), freq=round(effectif*100/Tot,2)) %>% 
    distinct(Gergraphic.localization, Species, `Statut Wolbachia`,.keep_all = TRUE)
  
## Calcul de l'intervalle de confiance
  db$yminn=NA
  db$ymaxx=NA
  
  
  for (i in 1:length(db$yminn)) {
    db$yminn[i]=round((prop.test(db$effectif[i],
                                 db$Tot[i],
                                 conf.level = 0.95)$conf.int[1]*100),2)
    
    db$ymaxx[i]=round((prop.test(db$effectif[i],
                                 db$Tot[i],
                                 conf.level = 0.95)$conf.int[2]*100),2)
  }

  db$Gergraphic.localization <- factor(db$Gergraphic.localization,levels = c("South","Center","North"))
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
# Diagramme en barres 
  plt <- ggplot(data=db,aes(x= Gergraphic.localization,y=freq, fill=`Statut Wolbachia`))+
    geom_bar(stat="identity", position = 'dodge', width = 0.7)+
    facet_wrap(~Species)+
    theme_bw()+geom_errorbar(aes(ymin=yminn,ymax=ymaxx),position = position_dodge2(width = 0.5, padding = 0.5))
  
  
  plt +
    scale_fill_manual(labels = aes(fill=`Statut Wolbachia`), 
                      values = c("black", "gray")) +
    labs(x="Gergraphic localization",
         y=expression("prevalence of "~italic(Wolbachia)~" %"))+
    theme(axis.text.x = element_text(angle = 45, hjust=1, size = 11, color = "black"),
          axis.title.x = element_text(size = 12, color="black"),
          axis.title.y = element_text(size = 12, color="black"),
          strip.text.x = element_text(size=12, color="black",face="italic"),
          axis.text.y = element_text(size = 11, color = "black"),
          legend.title = element_text(size = 12),
          panel.grid = element_blank())+
    guides(fill=guide_legend(title=" "))+
    scale_x_discrete(labels=c("South","Center","North"))
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
dbb <- filter(db,`Statut Wolbachia`=="Positive")
  
  plt1 <- ggplot(data=dbb,aes(x= Species,y=freq))+
    geom_bar(aes( fill=Gergraphic.localization), colour="black",stat="identity", position = position_dodge2(width = 0.5, padding = 0.5), width = 0.8)+
    geom_text(data=dbb,aes(label=freq, group=Gergraphic.localization), position = position_dodge(0.5),
              vjust = -0.3,hjust=0.3, size = 3.5)+
    scale_fill_manual(labels = aes(fill=Gergraphic.localization), 
                      values = c("black","white", "gray")) +
    theme_bw()#+geom_errorbar(aes(ymin=yminn,ymax=ymaxx,group=Capture_site),position = position_dodge2(width = 0.5, padding = 0.5))
  
  
  plt1 +labs(x="Gergraphic localization",
         y=expression("prevalence of "~italic(Wolbachia)~" %"),
         title = "Prevalence of species by geographical location")+
    theme(#axis.text.x = element_text(angle = 45, hjust=1, size = 11, color = "black"),
          axis.title.x = element_text(size = 12, color="black"),
          axis.title.y = element_text(size = 12, color="black"),
          strip.text.x = element_text(size=12, color="black",face="italic"),
          axis.text.y = element_text(size = 11, color = "black"),
          legend.title = element_text(size = 12),
          panel.grid = element_blank())+
    guides(fill=guide_legend(title=" "))+
    theme(legend.position = "bottom")
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
plt2 <- ggplot(data=dbb,aes(x= Species,y=freq))+
    geom_bar(aes( fill=Gergraphic.localization), colour="black",stat="identity", position = position_dodge2(width = 0.5, padding = 0.5), width = 0.8)+
    geom_text(data=dbb,aes(label=freq, group=Gergraphic.localization), position = position_dodge(0.5),
              vjust = -0.3,hjust=0.3, size = 3.5)+
    scale_fill_manual(labels = aes(fill=Gergraphic.localization), 
                      values = c("black","white", "gray")) +
    theme_bw()
  
  plt2 +labs(x="Gergraphic localization",
             y=expression("prevalence of "~italic(Wolbachia)~" %"),
             title = "Prevalence of species by geographical location")+
    theme(#axis.text.x = element_text(angle = 45, hjust=1, size = 11, color = "black"),
      axis.title.x = element_text(size = 12, color="black"),
      axis.title.y = element_text(size = 12, color="black"),
      strip.text.x = element_text(size=12, color="black",face="italic"),
      axis.text.y = element_text(size = 11, color = "black"),
      legend.title = element_text(size = 12),
      panel.grid = element_blank())+
    guides(fill=guide_legend(title=" "))+
    theme(legend.position = "bottom")
  
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
 plt3 <- ggplot(data=dbb,aes(x= Gergraphic.localization,y=freq, fill=Gergraphic.localization))+
    geom_bar(stat="identity", position = 'dodge', width = 0.7, color="black")+
    geom_text(data=dbb,aes(label=freq, group=Gergraphic.localization), position = position_dodge(0.5),
              vjust = -0.3,hjust=0.3, size = 3.5)+
    facet_wrap(~Species)+ 
    theme_bw()+geom_errorbar(aes(ymin=yminn,ymax=ymaxx),
                             position = position_dodge2(width = 0.5, padding = 0.5))+
  theme(legend.position="bottom")
  
  plt3 +
    scale_fill_manual(labels = aes(fill=`Statut Wolbachia`), 
                      values = c("black","white", "gray")) +
    labs(x="Gergraphic localization",
         y=expression("prevalence of "~italic(Wolbachia)~" %"),
         title = "Prevalence of species by geographical location")+
    theme(axis.text.x = element_text(angle = 45, hjust=1, size = 11, color = "black"),
          axis.title.x = element_text(size = 12, color="black"),
          axis.title.y = element_text(size = 12, color="black"),
          strip.text.x = element_text(size=12, color="black",face="italic"),
          axis.text.y = element_text(size = 11, color = "black"),
          legend.title = element_text(size = 12),
          panel.grid = element_blank())+
    guides(fill=guide_legend(title=" "))+
    scale_x_discrete(labels=c("South","Center","North"))
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
plt4 <- ggplot(data=dbb,aes(x= Gergraphic.localization,y=freq, fill=Gergraphic.localization))+
    geom_bar(stat="identity", position = 'dodge', width = 0.7, color="black")+
    geom_text(data=dbb,aes(label=freq, group=Gergraphic.localization), position = position_dodge(0.5),
              vjust = -0.3,hjust=0.3, size = 3.5)+
    facet_wrap(~Species)+
    theme_bw()+ 
    theme(legend.position="bottom")
  
  plt4 +
    scale_fill_manual(labels = aes(fill=`Statut Wolbachia`), 
                      values = c("black","white", "gray")) +
    labs(x="Gergraphic localization",
         y=expression("prevalence of "~italic(Wolbachia)~" %"),
         title = "Prevalence of species by geographical location")+
    theme(axis.text.x = element_text(angle = 45, hjust=1, size = 11, color = "black"),
          axis.title.x = element_text(size = 12, color="black"),
          axis.title.y = element_text(size = 12, color="black"),
          strip.text.x = element_text(size=12, color="black",face="italic"),
          axis.text.y = element_text(size = 11, color = "black"),
          legend.title = element_text(size = 12),
          panel.grid = element_blank())+
    guides(fill=guide_legend(title=" "))+
    scale_x_discrete(labels=c("South","Center","North"))
  
```


# Sup
```{r}
# Manipulation des données
data_P.W_E <-  filter(bd, Species %in% c("Aedes aegypti","Anophele gambiae", 
                                                       "Culex quinquefasciatus"))
  
  
db <- data_P.W_E %>% 
    dplyr::group_by(Gergraphic.localization, Species)%>% 
    dplyr::mutate(Tot = n()) #%>% 
  
  db <- db %>% 
    dplyr::group_by(Gergraphic.localization, Species, `Statut Wolbachia`)%>% 
    dplyr::mutate(effectif = n(), freq=round(effectif*100/Tot,2)) %>% 
    distinct(Gergraphic.localization, Species, `Statut Wolbachia`,.keep_all = TRUE) %>% filter(`Statut Wolbachia`=="Positive")
  
## Calcul de l'intervalle de confiance
  db$yminn=NA
  db$ymaxx=NA
  
  
  for (i in 1:length(db$yminn)) {
    db$yminn[i]=round((prop.test(db$effectif[i],
                                 db$Tot[i],
                                 conf.level = 0.95)$conf.int[1]*100),2)
    
    db$ymaxx[i]=round((prop.test(db$effectif[i],
                                 db$Tot[i],
                                 conf.level = 0.95)$conf.int[2]*100),2)
  }

  db$Gergraphic.localization <- factor(db$Gergraphic.localization,levels = c("South","Center","North"))
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Diagramme en barres 
  plt4 <- ggplot(data=db,aes(x= Gergraphic.localization,y=freq, fill=Gergraphic.localization))+
    geom_bar(stat="identity", position = 'dodge', width = 0.7, color="black")+
    #geom_text(data=db,aes(label=freq, group=Gergraphic.localization), position = position_dodge(0.5),
              #vjust = -0.3,hjust=0.3, size = 3.5)+
    facet_wrap(~Species)+
    theme_bw()+ geom_errorbar(aes(ymin=yminn,ymax=ymaxx),
                             position = position_dodge2(width = 0.5, padding = 0.5))+
    theme(legend.position="bottom")
  
  plt4 +
    scale_fill_manual(labels = aes(fill=`Statut Wolbachia`), 
                      values = c("black","white", "gray")) +
    labs(x="Gergraphic localization",
         y=expression("prevalence of "~italic(Wolbachia)~" %"),
         title = "Prevalence of species by geographical location")+
    theme(axis.text.x = element_text(angle = 45, hjust=1, size = 11, color = "black"),
          axis.title.x = element_text(size = 12, color="black"),
          axis.title.y = element_text(size = 12, color="black"),
          strip.text.x = element_text(size=12, color="black",face="italic"),
          axis.text.y = element_text(size = 11, color = "black"),
          legend.title = element_text(size = 12),
          panel.grid = element_blank())+
    guides(fill=guide_legend(title=" "))+
    scale_x_discrete(labels=c("South","Center","North"))
```
